\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-31 Paper/Paper.tex
use nolinkurl; cancel table numbering

\documentclass{article}
\usepackage{ctex}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{caption}
\RequirePackage{longtable,multirow,array}
\RequirePackage{booktabs}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage[style=ieee,sorting=nyt]{biblatex}
\assignrefcontextentries[]{*}
\addbibresource{References.bib}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\hypersetup{hidelinks}
\hypersetup{bookmarksnumbered=true,
	bookmarksopen=true,
	colorlinks=true,
	linkcolor=black,
	citecolor=blue,
	urlcolor=black}
\usepackage{tikz}
\usepackage{pgfplotstable}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\captionsetup{justification=centering}
\captionsetup[figure]{name={Fig.},labelsep=space,labelfont=bf}
\captionsetup[table]{name={Table},labelsep=space,labelfont=bf}
\CTEXoptions[today=old, contentsname=Contents]
\newcommand{\authyear}[1]{\citeauthor{#1} (\citeyear{#1})}
\setmainfont{Arial}

@@

	\subsection*{Results Page}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/Temp.png}
		\caption{Result Page}
		\vspace{0.3cm}
		\label{fig:result_page}
	\end{figure}

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{llp{9.5cm}}
				\caption{OCT Abnormities}
				\label{tb:oct-abnormites}\\
				\toprule
				Abnormity&Abbr.&Description\\
				\toprule

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{llp{11.2cm}}
				\caption{Fundus Abnormalities}
				\label{tb:fundus-ab}\\
				\toprule
				Abnormity&Abbr.&Description\\
				\toprule

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{cc}
				\caption{Diseases}
				\label{tb:diseases}\\
				\toprule
				Disease&Abbr.\\
				\toprule

@@

	\fontsize{6}{0}\selectfont{
	\begin{enumerate}
		\item \url{https://qers.com.au/eye-conditions/epiretinal-membrane-erm/}

		\item \url{https://www.asrs.org/patients/retinal-diseases/19/epiretinal-membranes}

		\item \url{https://theretinagroup.com/epiretinal-membrane/}

		\item \url{https://www.istanbulretina.com/en-diseases-epiretinal-membrane.php}

		\item \url{https://www.mdfoundation.com.au/about-macular-disease/other-macular-conditions/epiretinal-membrane-macular-pucker/}

		\item \url{https://www.researchgate.net/figure/Grading-of-epiretinal-membrane-ERM-by-spectral-domain-optical-coherence-tomography_fig1_351426760}

		\item \url{https://www.singhealth.com.sg/patient-care/conditions-treatments/epiretinal-membrane}

		\item \url{https://www.windycityretina.com/epiretinal-membrane/}

		\item \url{https://retinacentertx.com/conditions/macular-pucker}

		\item \url{https://www.rvscny.com/patient-eduction/conditions-we-treat/epiretinal-membrane/}

		\item \url{https://www.lyneye.co.za/epiretinal-membrane-erm/}

		\item \url{https://rehmansiddiqui.com/epi-retinal-membrane-erm/}

		\item \url{https://www.reviewofophthalmology.com/article/when-and-how-to-peel-an-epiretinal-membrane}

		\item \url{https://www.janigianretina.com/retina-conditions/epiretinal-membrane}

		\item \url{https://www.researchgate.net/figure/6-months-later-ERM-with-partial-attachment-to-the-retina_fig2_309566437}

		\item \url{https://www.capefearretina.com/epiretinal-membrane/}
	\end{enumerate}
	}

@@

	\fontsize{6}{0}\selectfont{
	\begin{enumerate}
			\item \url{https://emedicine.medscape.com/article/1224320-overview}

			\item \url{https://www.chatswoodeye.com/macular-hole-specialists/}

			\item \url{https://swretina.com/macular-hole/}

			\item \url{https://www.ophthalmologyexpertservices.com/blog/2019/macular-hole}

			\item \url{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}

			\item \url{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}

			\item \url{https://www.reviewofoptometry.com/article/facedown-showdown}

			\item \url{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}

			\item \url{https://www.researchgate.net/figure/Fundus-image-of-the-right-eye-of-case-1-a-shows-a-macular-hole-with-associated-retinal_fig1_324657341}

			\item \url{https://www.girayersoz.com.tr/en/macular-hole/}

			\item \url{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}

			\item \url{https://www.gotzaridis.gr/en/conhttps://www.willseye.org/macular-hole/ditions/macula/full-thickness-macular-hole}

			\item \url{https://www.willseye.org/macular-hole/}

			\item \url{http://www.oculist.net/downaton502/prof/ebook/duanes/pages/v3/ch031/013f.html}

			\item \url{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#11}

			\item \url{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#12}

			\item \url{https://www.jaypeedigital.com/book/9788180616532/chapter/ch7}

			\item \url{https://emedicine.medscape.com/article/1224320-clinical?form=fpf}

			\item \url{https://www.jaafarelannanmd.com/macular-hole}

			\item \url{https://asiaeyecentre.com.sg/eye-conditions/the-ageing-eye/macular-hole/}

			\item \url{https://retinaandeye.com.au/eye-conditions/full-thickness-macular-holes/}

			\item \url{https://retinahi.com/interesting-cases/}

			\item \url{https://imagebank.asrs.org/file/2858/traumatic-macular-hole}

			\item \url{https://www.semanticscholar.org/paper/Giant-macular-hole-as-an-atypical-consequence-of-a-Blaise-Comhaire/5c9a60375d904323eb5fbcd52b6bd03b735f6951}

			\item \url{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/Macular-hole-commotio-retinae-choroidal-rupture.htm#gsc.tab=0}

			\item \url{https://areaoftalmologica.com/en/terms-of-ophthalmology/macular-hole/}

			\item \url{https://www.reviewofoptometry.com/article/facedown-showdown}

			\item \url{https://montanaretinaconsultants.com/portfolio/macular-holes/}

			\item \url{https://ccteyes.com/2019/09/30/what-is-a-macular-hole-and-how-does-it-affect-your-vision/}

			\item \url{https://www.backoftheeyemd.com/retina-services/macular-holes/}

			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}

			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}

			\item \url{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}

			\item \url{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/extrafoveal-macular-hole/emh-1.jpg}
	\end{enumerate}
	}

@@

	\fontsize{6}{0}\selectfont{
		\begin{enumerate}
			\item \url{https://imagebank.asrs.org/file/93471/retinitis-pigmentosa}

			\item \url{https://educate.choroida.com/2021/07/05/retinitis-pigmentosa/}

			\item \url{https://decisionmakerplus.net/dg-post/h35-52-retinitis-pigmentosa/}

			\item \url{https://basicmedicalkey.com/retinitis-pigmentosa/}

			\item \url{https://www.news-medical.net/health/What-is-Retinitis-Pigmentosa.aspx}

			\item \url{https://www.researchgate.net/figure/Fundus-photograph-of-an-individual-affected-with-retinitis-pigmentosa-The-fundus_fig3_40447070}

			\item \url{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F15/}

			\item \url{https://www.brainkart.com/article/Retinal-Dystrophies--Retinitis-Pigmentosa_26087/}

			\item \url{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}

			\item \url{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}

			\item \url{https://retinography.org/sector-retinitis-pigmentosa/}

			\item \url{https://retinography.org/sector-retinitis-pigmentosa/}

			\item \url{https://www.linkedin.com/posts/stevenlevymd_blindness-from-retinitis-pigmentosa-reversed-activity-7047214648877608960-ar4h}

			\item \url{https://atlas-1-elastic.atlasoph.com/photo.jsf;jsessionid=94EF0B6B067E676E8BCB3F2AD7B9885A?node=6475&locale=en}

			\item \url{https://dizziness-and-balance.com/disorders/visual/retinopathy/RP.html}

			\item \url{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}

			\item \url{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}

			\item \url{https://eyeandear.org/2020/07/a-new-era-in-retinal-research/}

			\item \url{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F14/}

			\item \url{https://commons.wikimedia.org/wiki/File:Fundus_of_patient_with_retinitis_pigmentosa,_end_stage.jpg}

			\item \url{https://healthjade.net/retinitis-pigmentosa/}

			\item \url{https://www.reviewofoptometry.com/article/night-spots}

			\item \url{https://www.visualsurgery.com/eye-conditions/retinal-diseases/other-retinal-diseases/retinitis-pigmentosa/}

			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

			\item \url{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

			\item \url{https://emedicine.medscape.com/article/1227488-overview?form=basic}

			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}

			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}

			\item \url{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}

			\item \url{https://webvision.med.utah.edu/book/electrophysiology/the-electroretinogram-clinical-applications/}

			\item \url{https://www.retinarevealed.com/retinitis-pigmentosa-page-34-of-49/}

			\item \url{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}

			\item \url{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}

			\item \url{https://www.nyp.org/advances/article/ophthalmology/retinitis-pigmentosa-mitigating-retinal-degeneration-with-crispr-technology}

			\item \url{https://www.ehu.eus/en/-/pacientes-con-retinosis-pigmentaria-en-la-pole}

			\item \url{https://en.wikipedia.org/wiki/Retinal_degeneration_%28rhodopsin_mutation%29}

			\item \url{https://imagebank.asrs.org/file/29807/x-linked-retinitis-pigmentosa}

			\item \url{https://educate.choroida.com/2023/04/07/choroideremia-unveiling-what-you-need-to-know/}

			\item \url{https://retinography.org/retinitis-pigmentosa-2/}

			\item \url{https://retinography.org/retinitis-pigmentosa-2/}

			\item \url{https://retinography.org/retinitis-pigmentosa/}

			\item \url{https://retinography.org/retinitis-pigmentosa/}
		\end{enumerate}
	}

>>>>

\documentclass{article}
\usepackage{ctex}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{caption}
\RequirePackage{longtable,multirow,array}
\RequirePackage{booktabs}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{longtable}
\usepackage{xurl}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage[style=ieee,sorting=nyt]{biblatex}
\assignrefcontextentries[]{*}
\addbibresource{References.bib}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\hypersetup{hidelinks}
\hypersetup{bookmarksnumbered=true,
	bookmarksopen=true,
	colorlinks=true,
	linkcolor=black,
	citecolor=blue,
	urlcolor=black}
\usepackage{tikz}
\usepackage{pgfplotstable}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\captionsetup{justification=centering}
\captionsetup[figure]{name={Fig.},labelsep=space,labelfont=bf}
\captionsetup[table]{name={Table},labelsep=space,labelfont=bf}
\CTEXoptions[today=old, contentsname=Contents]
\newcommand{\authyear}[1]{\citeauthor{#1} (\citeyear{#1})}
\setmainfont{Arial}

@@

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{llp{9.5cm}}
				\caption*{OCT Abnormities}
				\label{tb:oct-abnormites}\\
				\toprule
				Abnormity&Abbr.&Description\\
				\toprule

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{llp{11.2cm}}
				\caption*{Fundus Abnormalities}
				\label{tb:fundus-ab}\\
				\toprule
				Abnormity&Abbr.&Description\\
				\toprule

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{cc}
				\caption*{Diseases}
				\label{tb:diseases}\\
				\toprule
				Disease&Abbr.\\
				\toprule

@@

	\begin{enumerate}
		\item \nolinkurl{https://qers.com.au/eye-conditions/epiretinal-membrane-erm/}

		\item \nolinkurl{https://www.asrs.org/patients/retinal-diseases/19/epiretinal-membranes}

		\item \nolinkurl{https://theretinagroup.com/epiretinal-membrane/}

		\item \nolinkurl{https://www.istanbulretina.com/en-diseases-epiretinal-membrane.php}

		\item \nolinkurl{https://www.mdfoundation.com.au/about-macular-disease/other-macular-conditions/epiretinal-membrane-macular-pucker/}

		\item \nolinkurl{https://www.researchgate.net/figure/Grading-of-epiretinal-membrane-ERM-by-spectral-domain-optical-coherence-tomography_fig1_351426760}

		\item \nolinkurl{https://www.singhealth.com.sg/patient-care/conditions-treatments/epiretinal-membrane}

		\item \nolinkurl{https://www.windycityretina.com/epiretinal-membrane/}

		\item \nolinkurl{https://retinacentertx.com/conditions/macular-pucker}

		\item \nolinkurl{https://www.rvscny.com/patient-eduction/conditions-we-treat/epiretinal-membrane/}

		\item \nolinkurl{https://www.lyneye.co.za/epiretinal-membrane-erm/}

		\item \nolinkurl{https://rehmansiddiqui.com/epi-retinal-membrane-erm/}

		\item \nolinkurl{https://www.reviewofophthalmology.com/article/when-and-how-to-peel-an-epiretinal-membrane}

		\item \nolinkurl{https://www.janigianretina.com/retina-conditions/epiretinal-membrane}

		\item \nolinkurl{https://www.researchgate.net/figure/6-months-later-ERM-with-partial-attachment-to-the-retina_fig2_309566437}

		\item \nolinkurl{https://www.capefearretina.com/epiretinal-membrane/}
	\end{enumerate}

@@

	\begin{enumerate}
			\item \nolinkurl{https://emedicine.medscape.com/article/1224320-overview}

			\item \nolinkurl{https://www.chatswoodeye.com/macular-hole-specialists/}

			\item \nolinkurl{https://swretina.com/macular-hole/}

			\item \nolinkurl{https://www.ophthalmologyexpertservices.com/blog/2019/macular-hole}

			\item \nolinkurl{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}

			\item \nolinkurl{https://www.researchgate.net/publication/38109568_Bilateral_macular_hole_secondary_to_remote_lightning_strike}

			\item \nolinkurl{https://www.reviewofoptometry.com/article/facedown-showdown}

			\item \nolinkurl{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}

			\item \nolinkurl{https://www.researchgate.net/figure/Fundus-image-of-the-right-eye-of-case-1-a-shows-a-macular-hole-with-associated-retinal_fig1_324657341}

			\item \nolinkurl{https://www.girayersoz.com.tr/en/macular-hole/}

			\item \nolinkurl{https://www.gotzaridis.gr/en/conditions/macula/full-thickness-macular-hole}

			\item \nolinkurl{https://www.gotzaridis.gr/en/conhttps://www.willseye.org/macular-hole/ditions/macula/full-thickness-macular-hole}

			\item \nolinkurl{https://www.willseye.org/macular-hole/}

			\item \nolinkurl{http://www.oculist.net/downaton502/prof/ebook/duanes/pages/v3/ch031/013f.html}

			\item \nolinkurl{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#11}

			\item \nolinkurl{https://www.slideshare.net/slideshow/macular-hole-227845841/227845841#12}

			\item \nolinkurl{https://www.jaypeedigital.com/book/9788180616532/chapter/ch7}

			\item \nolinkurl{https://emedicine.medscape.com/article/1224320-clinical?form=fpf}

			\item \nolinkurl{https://www.jaafarelannanmd.com/macular-hole}

			\item \nolinkurl{https://asiaeyecentre.com.sg/eye-conditions/the-ageing-eye/macular-hole/}

			\item \nolinkurl{https://retinaandeye.com.au/eye-conditions/full-thickness-macular-holes/}

			\item \nolinkurl{https://retinahi.com/interesting-cases/}

			\item \nolinkurl{https://imagebank.asrs.org/file/2858/traumatic-macular-hole}

			\item \nolinkurl{https://www.semanticscholar.org/paper/Giant-macular-hole-as-an-atypical-consequence-of-a-Blaise-Comhaire/5c9a60375d904323eb5fbcd52b6bd03b735f6951}

			\item \nolinkurl{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/Macular-hole-commotio-retinae-choroidal-rupture.htm#gsc.tab=0}

			\item \nolinkurl{https://areaoftalmologica.com/en/terms-of-ophthalmology/macular-hole/}

			\item \nolinkurl{https://www.reviewofoptometry.com/article/facedown-showdown}

			\item \nolinkurl{https://montanaretinaconsultants.com/portfolio/macular-holes/}

			\item \nolinkurl{https://ccteyes.com/2019/09/30/what-is-a-macular-hole-and-how-does-it-affect-your-vision/}

			\item \nolinkurl{https://www.backoftheeyemd.com/retina-services/macular-holes/}

			\item \nolinkurl{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}

			\item \nolinkurl{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}

			\item \nolinkurl{https://www.asrs.org/content/images/cms/image_rib_macularhole_2_2858.jpg/image-full;size$250,194.ImageHandler}

			\item \nolinkurl{https://webeye.ophth.uiowa.edu/eyeforum/atlas/pages/extrafoveal-macular-hole/emh-1.jpg}
	\end{enumerate}

@@

	\begin{enumerate}
		\item \nolinkurl{https://imagebank.asrs.org/file/93471/retinitis-pigmentosa}

		\item \nolinkurl{https://educate.choroida.com/2021/07/05/retinitis-pigmentosa/}

		\item \nolinkurl{https://decisionmakerplus.net/dg-post/h35-52-retinitis-pigmentosa/}

		\item \nolinkurl{https://basicmedicalkey.com/retinitis-pigmentosa/}

		\item \nolinkurl{https://www.news-medical.net/health/What-is-Retinitis-Pigmentosa.aspx}

		\item \nolinkurl{https://www.researchgate.net/figure/Fundus-photograph-of-an-individual-affected-with-retinitis-pigmentosa-The-fundus_fig3_40447070}

		\item \nolinkurl{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F15/}

		\item \nolinkurl{https://www.brainkart.com/article/Retinal-Dystrophies--Retinitis-Pigmentosa_26087/}

		\item \nolinkurl{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}

		\item \nolinkurl{https://entokey.com/retinitis-pigmentosa-and-allied-disorders/}

		\item \nolinkurl{https://retinography.org/sector-retinitis-pigmentosa/}

		\item \nolinkurl{https://retinography.org/sector-retinitis-pigmentosa/}

		\item \nolinkurl{https://www.linkedin.com/posts/stevenlevymd_blindness-from-retinitis-pigmentosa-reversed-activity-7047214648877608960-ar4h}

		\item \nolinkurl{https://atlas-1-elastic.atlasoph.com/photo.jsf;jsessionid=94EF0B6B067E676E8BCB3F2AD7B9885A?node=6475&locale=en}

		\item \nolinkurl{https://dizziness-and-balance.com/disorders/visual/retinopathy/RP.html}

		\item \nolinkurl{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}

		\item \nolinkurl{https://disorders.eyes.arizona.edu/disorders/retinitis-pigmentosa-ar}

		\item \nolinkurl{https://eyeandear.org/2020/07/a-new-era-in-retinal-research/}

		\item \nolinkurl{https://www.ncbi.nlm.nih.gov/books/NBK11553/figure/ch36clinicalerg.F14/}

		\item \nolinkurl{https://commons.wikimedia.org/wiki/File:Fundus_of_patient_with_retinitis_pigmentosa,_end_stage.jpg}

		\item \nolinkurl{https://healthjade.net/retinitis-pigmentosa/}

		\item \nolinkurl{https://www.reviewofoptometry.com/article/night-spots}

		\item \nolinkurl{https://www.visualsurgery.com/eye-conditions/retinal-diseases/other-retinal-diseases/retinitis-pigmentosa/}

		\item \nolinkurl{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

		\item \nolinkurl{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

		\item \nolinkurl{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

		\item \nolinkurl{https://www.researchgate.net/figure/Fundus-of-an-RP-patient-at-different-stages-a-Image-of-a-normal-healthy-eye-b_fig4_279155571}

		\item \nolinkurl{https://emedicine.medscape.com/article/1227488-overview?form=basic}

		\item \nolinkurl{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}

		\item \nolinkurl{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}

		\item \nolinkurl{https://www.centreforeyehealth.com.au/retinitis-pigmentosa-extract/}

		\item \nolinkurl{https://webvision.med.utah.edu/book/electrophysiology/the-electroretinogram-clinical-applications/}

		\item \nolinkurl{https://www.retinarevealed.com/retinitis-pigmentosa-page-34-of-49/}

		\item \nolinkurl{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}

		\item \nolinkurl{http://www.pjo.com.pk/30/2/12.CR%20Sana%20Nadeem%20Corrected.htm}

		\item \nolinkurl{https://www.nyp.org/advances/article/ophthalmology/retinitis-pigmentosa-mitigating-retinal-degeneration-with-crispr-technology}

		\item \nolinkurl{https://www.ehu.eus/en/-/pacientes-con-retinosis-pigmentaria-en-la-pole}

		\item \nolinkurl{https://en.wikipedia.org/wiki/Retinal_degeneration_%28rhodopsin_mutation%29}

		\item \nolinkurl{https://imagebank.asrs.org/file/29807/x-linked-retinitis-pigmentosa}

		\item \nolinkurl{https://educate.choroida.com/2023/04/07/choroideremia-unveiling-what-you-need-to-know/}

		\item \nolinkurl{https://retinography.org/retinitis-pigmentosa-2/}

		\item \nolinkurl{https://retinography.org/retinitis-pigmentosa-2/}

		\item \nolinkurl{https://retinography.org/retinitis-pigmentosa/}

		\item \nolinkurl{https://retinography.org/retinitis-pigmentosa/}
	\end{enumerate}
